Thread Pool in GeckoDB/BOLSTER

### 2018-06-07 Presentations/Milestone3/presentation.tex
Fred did some awesome stuff

\begin{frame}
	\frametitle{Open issues}

\end{frame}

@@

>>>>

\begin{frame}
	\frametitle{Open issues}
	\begin{itemize}
		\item gtest still has some problems due to itself being implemented in C++
		\item some race condition may still occur
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Task Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			enqueue\_time & Time when the task was enqueued \\
			execution\_time & Time when the task execution begins \\
			complete\_time & Time when the task execution is finished \\
			\hline
		\end{tabular}
		\label{tab2}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Thread Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			waiting\_time & Time the thread spend waiting (ms) \\
			busy\_time & Time the thread spend executing tasks (ms)\\
			task\_count & Number of tasks the thread has executed \\
			\hline
		\end{tabular}
		\label{tab3}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Thread Pool Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			working\_time & Time the thread pool runs (ms) \\
			task\_complete\_count & Number of completed tasks \\
			task\_enqueued\_count & Number of enqueued tasks \\
			avg\_complete\_time & Average time span from enqueueing until \\
			& execution of tasks \\
			avg\_wait\_time & Average time of tasks spend in the queue \\
			\hline
		\end{tabular}
		\label{tab4}
	\end{center}
\end{frame}

\section{Paper Progress}
\begin{frame}
	\begin{center}
	\huge Paper Progress \normalsize	
	\end{center}
\end{frame}

\begin{frame}
	\begin{itemize}
		\item Introduction and Preliminaries mostly completed
		\item Implementation described, including our used concepts and basic ideas how to build and operate the pool
		\item Still required is the Evaluation(since we still need to perform it), the description of our testing environment and our final conclusion
	\end{itemize}
\end{frame}
